Make any stupid plot you want

### 2020-11-12 draft/sections/math.tex
more words

\subsubsection{Data}
We use Butler's visualization model built on the mathematics of fiber bundles \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and Spivak's schema like description of fibers \cite{spivakSIMPLICIALDATABASES} as the basis of our data model.  The components of the fiber bundle are:

\begin{center}
    \begin{tabular}{ c c c }
     term & mathematical definition & data container analog\\
      $K$ & base space along which the data lies & indexer \\
      $F$ & fiber space from which possible values are pulled & schema \\
      $E$ & trivial: $F= K \times F$, non-trivial \dots & 
    \end{tabular}
\end{center}

>>>>

\subsubsection{Data}
We are using Butler's visualization model built on the mathematics of fiber bundles \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and Spivak's schema like description of fibers \cite{spivakSIMPLICIALDATABASES} as the basis of our data model. Fiber bundles give us a way to disentangle the connectivity of the data (is it a timeseries, a map?) from the variables in the dataset (temperature). Building on Munzner's formulation of the former as keys and the latter as values \cite{munznerWhatDataAbstraction2014}, the data has implicit keys that lie in the $K$ basespace of the fiberbundle, while the labels for the keys (such as latitude and longitude) are variables of the dataset that lie in the fiber $F$.

%%%maybe this comes in a later API section....
\begin{center}
    \table{tab:fiberbundle}
    \begin{tabular}{ c c c }
     term & mathematical definition & data container analog\\
      $K$ & base space along which the data lies & indexer \\
      $F$ & fiber space from which possible values are pulled & schema \\
      $E$ & trivial: $F= K \times F$, non-trivial \dots & 
    \end{tabular}
\end{center}

\begin{figure}
    \lable{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Examples of simplexes that can be connected to make up a trivial total space $E = K\times F$.
    EX: data that both has a vertex & edge - find & visualize}
\end{figure}

In our data model, we encode the indexer as its simplex representation so that we can keep all variables of the fiber encoded on a simplex together \cite{butlerVisualizationModelBased1989}
